Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-04-26 ms.tex
added table of fit results.

\begin{deluxetable}{lrr}
\tablecaption{List of observations}\label{tab:photSummary}
\tablewidth{0pt}
\tablehead{
\colhead{Date} &
\colhead{Comment} \\
\colhead{UT} & \\
\colhead{Amplitude} & \\
 }
\startdata
2016-06-10 & Clouds	& \\
2016-06-12 & Clear 		& \\
2016-06-14 & Clear 		&\\
2016-07-12 & Clear 		&\\
2016-07-14 & Mostly clear	& \\
2016-07-16 & Clear 		& \\
\enddata
\tablenotetext{}{Summary of observations and conditions in this work.}
\end{deluxetable}

>>>>

\begin{deluxetable}{lrr}
\tablecaption{List of observations}\label{tab:photSummary}
\tablewidth{0pt}
\tablehead{
\colhead{Date} &
\colhead{Weather} &
\colhead{Amplitude} \\
\colhead{UT} & & \\
 }
\startdata
2016-06-10 & Clouds	& \nodata \\
2016-06-12 & Clear 		& 0.94 $\pm$ 0.16 \\
2016-06-14 & Clear 		&0.70 $\pm$ 0.18\\
2016-07-12 & Clear 		& 0.78 $\pm$ 0.14 \\
2016-07-14 & Mostly clear	& 1.33 $\pm$ 0.14 \\
2016-07-16 & Clear 		& 2.14 $\pm$ 0.19 \\
\enddata
\tablenotetext{}{Summary of observations and conditions in this work.}
\end{deluxetable}
